### 2017-03-01 prob.tex
further re-arragement

ALP introduces what is known as linear function approximation in the LP, i.e., the value function computed by ALP can be given by $\tj=\Phi \tr$ for an appropriate $\tr\in \R^k$. ALP is a linear program in $k$ ($<<n$) variables and hence is computationally easier to handle in practice than LP. Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP. In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ (the greedy policy with respect to $\tj$, see \Cref{notations}-\eqref{greedy}) where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}. Further, when convenient, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ in \eqref{alp} using the definition of $T$ from \Cref{notations}-\eqref{bellopval}.\\

@@

Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in the ALP. In the first approach \cite{CS}, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear programming} (RLP) problem. The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions. The second approach involves employing function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}. However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach. We now dicuss RLP and its error analysis.\\

@@

where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}. We denote an arbitrary solution to the RLP by $\tr_{RLP}$.\\

@@

\item In \eqref{mdplp}, \eqref{alp}, \eqref{rlp} and \eqref{grlp} $c>0 \in \R^n$ is a probability distribution.
\item The ALP \eqref{alp} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}. Note that in \eqref{alp}, $Phi r\geq T\Phi r$ is a shortcut to denote the $S\times A$ constraints. Also, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP. We denote an arbitrary solution to the ALP by $\tr\in \R^k$.\par
\item The RLP \eqref{rlp} was first introduced in \cite{CS}. The RLP \eqref{rlp} has the same objective function as the ALP \eqref{rlp}. The construction of the RLP needs three parameters to be specified namely, the number of samples $m$, the sampling distribution $\psi$ and the constraint set $\N$. In particular, $\psi=\psi(u^*)$ i.e., the sampling distribution
In the RLP in \eqref{rlp}, $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$. The samples are generated using a distribution $\psi$ (see a restatement of the results in \cite{CS} summarized in \Cref{}).
$\N$ is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}. We denote an arbitrary solution to the RLP by $\tr_{RLP}$. It is important to note that the RLP \eqref{rlp} is a random linear program, in the sense that it depends on the $m$ samples obtained from $\psi$.
\item In the GRLP in \eqref{grlp}, $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints. The RLP \eqref{rlp} can be recovered as a special case of the GRLP \cite{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$. The $\N$ in the RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well. For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP. We denote an arbitrary solution to the GRLP by $\hr$.
\end{enumerate}
In what follows, unless specified otherwise we use let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t. $\hj$/$\tj$.\par
\FloatBarrier
\input{cartoon}
\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively. The error in the ALP solution has already been studied in \cite{ALP}. Our objective is to study the extra source of error due to constraint approximation.
\end{comment}
\begin{comment}
In addition, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}

>>>>

ALP introduces what is known as linear function approximation in the LP, i.e., the value function computed by ALP can be given by $\tj=\Phi \tr$ for an appropriate $\tr\in \R^k$. ALP is a linear program in $k$ ($<<n$) variables and hence is computationally easier to handle in practice than LP. Note that, for $k=n$ and $\Phi=I_{n\times n}$, ALP is same as the LP. In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ (the greedy policy with respect to $\tj$, see \Cref{notations}-\eqref{greedy}) where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}. Further, when convenient, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ in \eqref{alp} using the definition of $T$ from \Cref{notations}-\eqref{bellopval}.\\

@@

Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in ALP. In the first approach \cite{CS}, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear programming} (RLP) problem. The performance analysis of RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions. The second approach involves employing function approximation in the dual variables of ALP \cite{ALP-Bor,dolgov}. However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach. We now dicuss RLP and its error analysis.\\

@@

where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of RLP \eqref{alp}. We denote an arbitrary solution to RLP by $\tr_{RLP}$.\\

@@

\item In \eqref{mdplp}, \eqref{alp}, \eqref{rlp} and \eqref{grlp} $c>0 \in \R^n$ is a probability distribution.
\item The ALP \eqref{alp} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}. Note that in \eqref{alp}, $Phi r\geq T\Phi r$ is a shortcut to denote the $S\times A$ constraints. Also, for $k=n$ and $\Phi=I_{n\times n}$, ALP is same as the LP. We denote an arbitrary solution to ALP by $\tr\in \R^k$.\par
\item The RLP \eqref{rlp} was first introduced in \cite{CS}. The RLP \eqref{rlp} has the same objective function as ALP \eqref{rlp}. The construction of RLP needs three parameters to be specified namely, the number of samples $m$, the sampling distribution $\psi$ and the constraint set $\N$. In particular, $\psi=\psi(u^*)$ i.e., the sampling distribution
In RLP in \eqref{rlp}, $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$. The samples are generated using a distribution $\psi$ (see a restatement of the results in \cite{CS} summarized in \Cref{}).
$\N$ is a compact set such that $\tr \in \N$, and it ensures boundedness of RLP \eqref{alp}. We denote an arbitrary solution to RLP by $\tr_{RLP}$. It is important to note that RLP \eqref{rlp} is a random linear program, in the sense that it depends on the $m$ samples obtained from $\psi$.
\item In the GRLP in \eqref{grlp}, $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints. The RLP \eqref{rlp} can be recovered as a special case of the GRLP \cite{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$. The $\N$ in RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well. For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as ALP. We denote an arbitrary solution to the GRLP by $\hr$.
\end{enumerate}
In what follows, unless specified otherwise we use let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t. $\hj$/$\tj$.\par
\FloatBarrier
\input{cartoon}
\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively. The error in ALP solution has already been studied in \cite{ALP}. Our objective is to study the extra source of error due to constraint approximation.
\end{comment}
\begin{comment}
In addition, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}
